### 2014-03-15 src/analysis.Rnw
Turn off redundant graphs

\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 20 (5\%)}
\label{fig:fullimgsize2}
\end{figure*}

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=

df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 10)
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 10 (10\%)}
\label{fig:fullimgsize3}
\end{figure*}

\begin{figure*}[t]
<<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=

df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 5)
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 5 (20\%)}
\label{fig:fullimgsize4}
\end{figure*}

>>>>

% \begin{figure*}[t]
% <<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
% @
% \caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 20 (5\%)}
% \label{fig:fullimgsize2}
% \end{figure*}
% 
% \begin{figure*}[t]
% <<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% 
% df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 10)
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
% @
% \caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 10 (10\%)}
% \label{fig:fullimgsize3}
% \end{figure*}
%

% \begin{figure*}[t]
% <<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% 
% df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 5)
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
% @
% \caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 5 (20\%)}
% \label{fig:fullimgsize4}
% \end{figure*}
%
